\documentclass[a4paper]{article}

\usepackage{setspace}
\usepackage[math-style=ISO, bold-style=ISO]{unicode-math}
\setmainfont{EB Garamond}
\setmathfont{Garamond-Math.otf}[StylisticSet={7,9}]
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{csvsimple}
\usepackage[super]{nth}
\usepackage{microtype}

\usepackage[backend=biber,
			style=apa]{biblatex}

\hypersetup{colorlinks=false,
			breaklinks=true}
\graphicspath{ {/home/michael-schmutzer/Documents/Projects/Ammonites/results/} }
\addbibresource{../../Ammonites.bib}

\title{Ammonoid Extinction and Nautilid Survival: Project report 4}
\date{\today}
\author{}

\begin{document}

\maketitle

%\setlength\parindent{0pt}
\onehalfspacing

What is the status of subgenera and can I ignore them? 


Analysis at the species level

Body size data is at genus level
Hatching size data is too incomplete. Only five ammonoid species actually extant at the end of the Maastrichtian have measurements, and none of the survivors.

Ammonites present at end of Maastrichtian. Species level. 
- Literature search and PBDB last occurrences. 
- Using a fairly strict cut-off, have to have occurrences in the latest Maastrichtian formations
- Geographic ranges are based on finds from throughout the Maastrichtian

Identifying survivorship in nautilids poses considerable challenges.
- Many genera cross the K-Pg boundary, but have different species before and after. Unclear what is descended from what
- The same species may be assigned a different name after the K-Pg, for example many Asian specimen of \textit{Eutrephoceras dekayi} are assigned to \textit{E. bellerophon} in the Danian. MALCHYK THESIS
- For many other nautilids, these relationships are less clear. 
- Currently these issues are causing me to underestimate the number of surviving nautilid genera
- I have used a less stringent cut-off for nautilids, because they are relatively rare compared to ammonites it is not clear to me if they went extinct before the end of the Maastrichtian or the sampling probability is just too low 

Cutting down dataset to species level.
- Keep only those occurrences that are classified to the species level
- Remove all occurrences of species not extant at the end of the Maastrichtian. Last occurrence on PBDB and literature search
- Resolve species synonymies. Give a list.
- Losing some taxa that are not resolved to species level, e.g. Nostoceras and Fresvillia

Taxonomy matters. The number of occurrences and the geographic range reconstructed from a handful of specimen can change substantially if these occurrences are classified in a different way. 
- Problems with sexual dimorphism, eg Menuites being the microconch, Anapachydiscus the macroconch of the same species COBBAN AND KENNEDY 1993

Data problems
- Low resolution at stage level of PBDB makes it seem like species that followed each other in rapid succession actually coexisted

Results



How to communicate sensitivity analyses?
- Different plate tectonic models
- Subsampling results


\end{document}